\subsection{Development Methodology}
\input{../DevelopmentMethodology.tex}

\subsection{Informing the Client}
\begin{itemize}
	\item Since the client is on site we will want to have bi-weekly meetings where we will report on what has been done in the past week and suggest and discuss what will be done in the coming week. This is also in line with die aglie development methodology that has been chosen.
	\item Email will be used if the team has questions for the client that can not wait until the next meeting.
	\item The client may potentially have access to a scrum server the developers are using for the project.
\end{itemize}

\subsection{Initial Ideas on Solving Some Technical Challenges}
\begin{itemize}
	\item Use a REST service for the web interface.
	\item Using git to roll out production code, and separate this from development code.
	\item Use Android Studio's built in emulation device to test the application if time permits us to build it.
\end{itemize}

\subsection{Technologies We will Use}
\begin{itemize}
	\item Spring\\
	For dependancy injection and Aspect Oriented Programming.
	\item Java\\
	For the main development of the backend, including the matching al
	\item AngularJS
	\item This will be combined into a monolithic architecture\\
\end{itemize}

\subsection{What Will The Client Receive}
On completion of the development cycle the client will receive the following:
\begin{itemize}
	\item The functional application, which includes:
	\begin{itemize}
		\item The functioning web interface
		\item The backend which will run the logic required to determine the teams for the next round of the Rocking the boat" exercise of the Software Engineering module
		\item Possibly a basic android application depending on the avaiable time
	\end{itemize}
	\item The source code for the functional application
	\item Associated build files
	\item The source code for all unit and integration tests
	\item The completed Requirements Specification document for the system
	\item All other documentation as required by the agile development methodology
	\item (possibly) a simple user manual, but hopefully the web interface will be intuitive enouch that this will not be nessesary	
\end{itemize}